Lawvere-Tierney Sheafification\\ in Homotopy Type Theory

### 2015-01-19 paper/sheaf_lics.tex
minor correction

%
If Coq handles cumulativity on all $\Type$ natively, it is not
the case for the $\Sigma$-type $\Type_n$, which require propositional
resizing. 
%
This issue could be solved by adding an axiom of cumulativity
for $\Type_n$ with an explicit management of universes. 
%
But as it would not have any computational content, such a solution
would really complicate the proofs as the axiom would appear
everywhere cumulativity is needed and it would need explicitly
annotation for universe levels everywhere in the formalization.

We have chosen a more simple but maybe less satisfactory solution. 
%
When the absence of cumulativity on $\Type_n$ rises a universe issue
for a lemma, we have proven the lemma and then admit the exact same
lemma, just letting Coq infer less constrained universe levels.

An other issue with universe polymorphism lies in their management for
recursive definitions. Indeed, the following recursive definition of
sheafification:
%
\[ \begin{array}{l}
   \modal : \forall \ (n : nat), \ \Type_n \to \Type_n 
   \\
    \modal_{-1\phantom{n}} \defeq \lambda T:\HProp,~ \lnot\lnot T \\
      \displaystyle{\modal_{n+1} \defeq  \lambda T:\Type_{n+1}},\\
      \hspace{5em} \displaystyle{\sum_{u:T \to \Type_n^\modal} \modal_{-1} 
      \left\|
      \sum_{a:T} u= (\lambda t,~\modal_n (a=t))
      \right\|}
    \end{array}
\]
%
is not allowed. 
%
This is because Coq forces the universe of the first $\Type_n$
occurring to be the same for every $n$, whereas the universe of the
$\Type_{n+1}$ occurring in $\modal_{n+1}$ should be at least one level
higher as the one of $\Type_n$ occurring in $\modal_{n+1}$ because of
the use of $\Sigma$-type over $T \to \Type_n^\modal$.
%
% \nt{explain why it is an issue.}
%
Thus, the induction step presented in this paper has been formalized,
but the complete recursive sheafification can not be defined for the
moment.
%
This restriction in our formalization can not be solved without
generalizing universe polymorphism for recursive definition.
%

>>>>

%
If Coq handles cumulativity on all $\Type$ natively, it is not
the case for the $\Sigma$-type $\Type_n$, which require propositional
resizing. 
%
This issue could be solved by adding an axiom of cumulativity
for $\Type_n$ with an explicit management of universes. 
%
But as it would not have any computational content, such a solution
would really complicate the proofs as the axiom would appear
everywhere cumulativity is needed and it would need explicitly
annotation for universe levels everywhere in the formalization.
%
We have chosen a more simple but maybe less satisfactory solution. 
%
When the absence of cumulativity on $\Type_n$ rises a universe issue
for a lemma, we have proven the lemma and then admit the exact same
lemma, just letting Coq infer less constrained universe levels.

An other issue with universe polymorphism lies in the management of
recursive definitions. Indeed, the following recursive definition of
sheafification
%
\[ \begin{array}{l}
   \modal : \forall \ (n : nat), \ \Type_n \to \Type_n 
   \\
    \modal_{-1\phantom{n}} \defeq \lambda T:\HProp,~ \lnot\lnot T \\
      \displaystyle{\modal_{n+1} \defeq  \lambda T:\Type_{n+1}},\\
      \hspace{5em} \displaystyle{\sum_{u:T \to \Type_n^\modal} \modal_{-1} 
      \left\|
      \sum_{a:T} u= (\lambda t,~\modal_n (a=t))
      \right\|}
    \end{array}
\]
%
is not allowed. 
%
This is because Coq forces the universe of the first $\Type_n$
occurring in the definition to be the same for every $n$, whereas the
universe of the first $\Type_{n+1}$ occurring in $\modal_{n+1}$ should be at
least one level higher as the one of $\Type_n$ occurring in
$\modal_{n}$ because of the use of $\Sigma$-type over
$T \to \Type_n^\modal$.
%
% \nt{explain why it is an issue.}
%
Thus, the induction step presented in this paper has been formalized,
but the complete recursive sheafification can not be defined for the
moment.
%
This restriction in our formalization can not be solved without
generalizing universe polymorphism for recursive definition.
%
